% Copyright (c) 2011-2014, Corey Oliver, corey.jon.oliver@gmail.com

% Permission to use, copy, modify, and/or distribute this software for
% any purpose with or without fee is hereby granted, provided that the
% above copyright notice and this permission notice appear in all
% copies.

% THE SOFTWARE IS PROVIDED “AS IS” AND THE AUTHOR DISCLAIMS ALL
% WARRANTIES WITH REGARD TO THIS SOFTWARE INCLUDING ALL IMPLIED
% WARRANTIES OF MERCHANTABILITY AND FITNESS. IN NO EVENT SHALL THE
% AUTHOR BE LIABLE FOR ANY SPECIAL, DIRECT, INDIRECT, OR CONSEQUENTIAL
% DAMAGES OR ANY DAMAGES WHATSOEVER RESULTING FROM LOSS OF USE, DATA OR
% PROFITS, WHETHER IN AN ACTION OF CONTRACT, NEGLIGENCE OR OTHER
% TORTIOUS ACTION, ARISING OUT OF OR IN CONNECTION WITH THE USE OR
% PERFORMANCE OF THIS SOFTWARE.

% Jason R. Blevins - Curriculum Vitae
% 
% Copyright (C) 2004-2011 Jason R. Blevins
% 
% You may use use this document as a template to create your own CV
% and you may redistribute the source code freely.  No attribution is
% required in any resulting documents.  I do ask that you please leave
% this notice and the above URL in the source code if you choose to
% redistribute this file.

\documentclass[11pt,letterpaper]{article}

\usepackage{hyperref}
\usepackage{geometry}

% Fonts
\usepackage[T1]{fontenc}
% \usepackage[urw-garamond]{mathdesign}

% Set your name here
\def\name{Hannah C. Oliver}

% The following metadata will show up in the PDF properties
\hypersetup{
  colorlinks = true,
  urlcolor = black,
  pdfauthor = {\name},
  pdfkeywords = {doctor of osteopathic medicine},
  pdftitle = {\name: Resume},
  pdfsubject = {Resume},
  pdfpagemode = UseNone
}

\geometry{
  body={6.5in, 9.0in},
  left=1.0in,
  top=1.0in
}

% Customize page headers
\pagestyle{myheadings}
\markright{\name}
\thispagestyle{empty}

% Custom section fonts
\usepackage{sectsty}
\sectionfont{\rmfamily\bfseries\large}
\subsectionfont{\rmfamily\mdseries\itshape\normalsize}

% Other possible font commands include:
% \mdseries for default,
% \ttfamily for teletype,
% \sffamily for sans serif,
% \bfseries for bold,
% \scshape for small caps,
% \normalsize, \large, \Large, \LARGE sizes.

% Don't indent paragraphs.
\setlength\parindent{0em}

% Make lists without bullets and compact spacing
\renewenvironment{itemize}{
  \begin{list}{}{
      \setlength{\leftmargin}{1.5em}
      \setlength{\itemsep}{0.25em}
      \setlength{\parskip}{0pt}
      \setlength{\parsep}{0.25em}
    }
  }{
  \end{list}
}

% Make lists with bullets
\newenvironment{bitemize}{
  \begin{list}{$\bullet$}{
      \setlength{\leftmargin}{1.5em}
      \setlength{\itemsep}{0.25em}
      \setlength{\parskip}{0pt}
      \setlength{\parsep}{0.25em}
    }
  }{
  \end{list}
}

\newcommand{\yearrange}[1]{\hfill \textbf{#1} \par}

\begin{document}

% Place name at left
% {\huge \name}

% Alternatively, print name centered and bold:
\centerline{\huge \bf \name}

\bigskip

\begin{minipage}[t]{0.5\textwidth}
  2742 Fleur Drive  Apt. 313 \\
  Des Moines, IA 50321
\end{minipage}
\begin{minipage}[t]{0.5\textwidth}
  \hfill Phone: (515) 210-9494\\
  \hspace*{0pt} \hfill Email: \href{mailto:hannah.christine.oliver@gmail.com}{hannah.christine.oliver@gmail.com}
\end{minipage}

\section*{Education}

\begin{itemize}
\item \textbf{Doctor of Osteopathic Medicine} Des Moines University \yearrange{Expected May 2015}
\item \textbf{Bachelor of Arts in Biology}  \textit{Cum Laude}, Central College, Pella, IA
  College \yearrange{May 2011}
  \begin{itemize} 
  \item {Study Abroad:} London, England, Spring 2010
  \end{itemize}
\end{itemize}

\section*{Honors and Awards}
\begin{itemize}
\item \textbf{Edward and Amanda Miller Scholarship} \yearrange{Spring 2012}
  \textit{Des Moines University}
  \begin{bitemize}
    \item Awarded to promising medical students with an interest in pediatrics.
  \end{bitemize}
\item \textbf{Dr. Herman Vander Meulen Award} \yearrange{Spring 2011}
  \textit{Central College}
  \begin{bitemize}
    \item Awarded for achievement to a student accepted to medical school.
  \end{bitemize}
	
\item \textbf{Presidential Scholarship} \yearrange{Fall 2007 -- Spring 2011}
  \textit{Central College}
  \begin{bitemize}
    \item Awarded to incoming freshman for high school achievement.
  \end{bitemize}
\end{itemize}

\section*{Service}
\subsection*{Pediatrics Club, Des Moines University}
\begin{itemize}
\item \textbf{President} \yearrange{Fall 2012 -- Spring 2013}
  \begin{bitemize}
  \item Led club meetings and organized volunteering
  \item Coordinated speakers including topics such as developmental
    pediatrics, genetics, having a child with special needs, how
    maternal stress during pregnancy affects infant biology,
    immunization myths.
  \item Organized a charity event for a emergency youth shelter
    collecting winter items and toys.
  \end{bitemize}
\item \textbf{First Year Liaison} \yearrange{Fall 2011 -- Spring 2012}
  \begin{bitemize}
  \item Created a monthly motor skills class to help children ages 0-2 years old with Down's Syndrome.
  \item Assisted senior club members with their responsibilities such as organizing fundraising and volunteer events.
  \end{bitemize}
\end{itemize}

\subsection*{Admission Office, Des Moines University}
\begin{itemize}
\item \textbf{Prospective Student Interviewer} \yearrange{Fall 2012 -- Spring 2013}
  \begin{bitemize}
  \item Interviewed prospective students applying to the osteopathic
    medicine program.
   \item Helped Admissions staff select medical school applicants based on fit with current student population and potential for success.
  \end{bitemize}
\end{itemize}

\subsection*{Psychiatry Club, Des Moines University}
\begin{itemize}
\item \textbf{Member} \yearrange{Fall 2012 -- Spring 2013}
  \begin{bitemize}
  \item Gave a presentation to fellow students on a journal article about autism to benefit group learning.
  \item Participated in group meetings.
   \end{bitemize}
\end{itemize}

\subsection*{OB/GYN Club, Des Moines University}
\begin{itemize}
\item \textbf{Member} \yearrange{Fall 2012 -- Spring 2013}
  \begin{bitemize}
  \item Participated in a workshop on birth control options and OB/GYN surgical skills. 
    \end{bitemize}
\end{itemize}

\subsection*{Gay Straight Alliance, Des Moines University}
\begin{itemize}
\item \textbf{Member} \yearrange{Fall 2012 -- Spring 2013}
  \begin{bitemize} 
 \item Participated in lecture on how to appropriately elicit a non-exclusive sexual history.
 \item Attending an LGBT Health Conference in April 2014 to learn how to improve health care inequities in this population and learn best care practices.
  \end{bitemize}
\end{itemize}


\section*{Research}

\subsection*{Des Moines University}
\begin{itemize}
\item \textbf{Student Researcher} \yearrange{Summer 2012}
  \textit{Dr. David Strom} (Mentor)
  \begin{bitemize}
  \item Analyzed angiogenic proteins expressed in Glioblastoma
    Multiforme utilizing tumor sample collection and analysis
    techniques. 
  \item Presented research project to other faculty and students.
  \end{bitemize}
\end{itemize}


\section*{Employment}

\subsection*{Madison County Memorial Hospital, Winterset, IA}
\begin{itemize}
\item \textbf{Certified Nursing Aide} \yearrange{Summer 2010}
  \begin{bitemize}
    \item Assisted patients with activities of daily living on Medical-Surgical Floor.
  \end{bitemize}
\end{itemize}

\subsection*{Care Center Nursing Home, Winterset, IA}
\begin{itemize}
\item \textbf{Certified Nursing Aide} \yearrange{Summer 2008}
  \begin{bitemize}
    \item Assisted residents with activities of daily living.
  \end{bitemize}
\end{itemize}

\end{document}
